---
title: "AFM-graphTypes"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{AFM-graphTypes}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(nanoscopeAFM)
library(ggplot2)
library(scales)
```

## Loading AFM image

```{r}
fname = AFM.getSampleImages()[1]
afmd = AFM.import(fname)
```

The AFM image can be displayed using graphTypes:

## graphType 1

This is the basic and default graph for an AFM image:

```{r}
plot(afmd, graphType=1)
```

## graphType 2

This graph has a square shape and adds a bar of length 20%; it places the scale inside the graph.

```{r}
plot(afmd, graphType=2)
```

The image can be saved with `ggsave` as it is graphed with ggplot.

```{r}
g1 = plot(afmd, graphType=2)
ggsave(tempfile(pattern = "", fileext = ".png"), plot=g1, dpi=300)
```

## graphType 3

This graph type is bare and has neither length scales nor legend.

```{r}
plot(afmd, graphType=3)
summary(afmd)
```


## graphing 2 plots side by side

Use the package `cowplot` to create a graph with two plots. Use `save_plot` to save the graph.

```{r}
library(cowplot)
fname2 = AFM.getSampleImages(type='ibw')[1]
afmd2 = AFM.import(fname2)
summary(afmd2)
g1 = plot(afmd, trimPeaks=0.01, graphType = 3)
g2 = plot(afmd2, no=2, trimPeaks=0.01, graphType = 3, mpt=29.6)
g3 = plot(afmd, no=3, trimPeaks=0.01, graphType = 3, mpt=65.5)
g4 = plot(afmd, no=4, trimPeaks=0.01, graphType = 3)
plot_grid(g1, g2, g3, g4,
          labels=c('A','B','C','D'))
```

